FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2024-08-08 paper.tex
jcon2: number → constant
jcon2: update JuliaHub URL

The flip side is that most real numbers fall into the gaps between \fp{} numbers and must be rounded, which introduces error
and can lead to surprising results.
For example, adding the tiny Planck constant to the large Avogadro number results in
the Avogadro number after rounding:

@@

\TF{} tracks exceptional values in Julia programs across
their \genpropkill{} lifetime and can fuzz code for vulnerabilities by
injecting a \Nan{} or \Inf{} as the result of an operation. \TF{} is
implemented in Julia as a library and is available on JuliaHub (TODO update link):

\noindent\begin{center}\noindent\!\!\url{https://juliahub.com/ui/Packages/FloatTracker/dBXig}\!\!
\end{center}

>>>>

The flip side is that most real numbers fall into the gaps between \fp{} numbers and must be rounded, which introduces error
and can lead to surprising results.
For example, adding the tiny Planck constant to the large Avogadro constant results in
the Avogadro constant after rounding:

@@

\TF{} tracks exceptional values in Julia programs across
their \genpropkill{} lifetime and can fuzz code for vulnerabilities by
injecting a \Nan{} or \Inf{} as the result of an operation. \TF{} is
implemented in Julia as a library and is available on JuliaHub:

\noindent\begin{center}\noindent\!\!\url{https://juliahub.com/ui/Packages/TrackedFloats}\!\!
\end{center}
